\documentclass[16pt]{article}



\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

 \geometry{
 a4paper,
 total={170mm,250mm},
 left=20mm,
 top=20mm,
 }

\pagenumbering{gobble}

\begin{document}

\noindent \textbf{Juho Alasalmi} \hfill{\textbf{Curriculum Vitae}} \par
\noindent  \hfill{\today} \par
\noindent Teaching and research assistant, Ph.D. candidate in the \href{https://www.wiwi.uni-konstanz.de/goldluecke/team/academic-staff/doctoral-students/}{\textcolor{blue}{University of Konstanz}} \par
\noindent Economist at \href{http://www.ptt.fi/}{\textcolor{blue}{Pellervo Economic Research}} \\

\noindent e-mail University of Konstanz: \href{mailto: juho.alasalmi@uni-konstanz.de}{\textcolor{blue}{juho.alasalmi@uni-konstanz.de}} \\
\noindent e-mail PTT: \href{mailto: juho.alasalmi@ptt.fi}{\textcolor{blue}{juho.alasalmi@ptt.fi}}\\
\noindent personal website: \href{https://jalasalmi.github.io}{\textcolor{blue}{https://jalasalmi.github.io}}

\subsection*{References}

\begin{tabular}{@{}p{2.2in}|p{2in}|p{2.3in}}
\textbf{Prof. Dr. Susanne Goldlücke}    &\textbf{Prof. Panu Poutvaara Ph.D.}   &  \textbf{Prof. Dr. Olli-Pekka Ruuskanen}  \\
University of Konstanz            &  Ifo Institute and                    & Pellervo Economic Research and \\
                                            & University of Munich                &  University of Vaasa   \\
susanne.goldluecke@uni-konstanz.de        &   Poutvaara@ifo.de   &     olli-pekka.ruuskanen@ptt.fi \\
\end{tabular}


\subsection*{Working Papers}

\noindent \textit{Self-Signaling and Voting for Redistribution} (Job market paper) \\ \href{https://jalasalmi.github.io/papers/signaling\_mobility\_prospects.pdf}{\textcolor{blue}{https://jalasalmi.github.io/papers/signaling\_mobility\_prospects.pdf}} \\

\noindent \textit{Contracted Labour Mobility and Self-selection on Job Match Quality} \\ \href{https://jalasalmi.github.io/papers/selection\_on\_job\_match\_quality.pdf}{\textcolor{blue}{https://jalasalmi.github.io/papers/selection\_on\_job\_match\_quality.pdf}} \\

\noindent \textit{Hidden Overtime: Optimal Contracts with (Self-)deceptive Effort Reports} \\
with Susanne Goldlücke and Michelle Jordan \\

% \noindent \textit{Motivated Prospects of Upward Mobility} \\ \href{https://jalasalmi.github.io/papers/mpoum.pdf}{\textcolor{blue}{https://jalasalmi.github.io/papers/mpoum.pdf}} \\

% \noindent \textit{The Effects of Vocational Labour Market Training: Evidence from Finland} \\ 
% with Henna Busk and Veera Holappa \\

\noindent For more see \href{https://jalasalmi.github.io/research.html}{\textcolor{blue}{https://jalasalmi.github.io/research.html}}

\subsection*{Awards} 
\begin{tabular}{@{}p{1.5in}p{5in}}
8/2018           & \textbf{Best Master's Thesis} in business and economics in the University of Tampere in academic year 2017-2018 \\
9/2022           & \textbf{Best paper award} RUCAM Workshop on Analytical Modelling Approaches to Understanding Democracy, Nijmegen. Paper: \textit{Self-signaling and Voting for Redistribution}. Award committee: Allan Drazen, Toke Aidt
\end{tabular}

\subsection*{Research Interests}

\begin{itemize} \setlength\itemsep{0.01em}
   \item Theoretical behavioral economics: optimal belief and self-esteem management with applications in public and labour economics.
   \item Theoretical and empirical labour economics: active labour market policy evaluation and spatial labour mobility.
\end{itemize}

\subsection*{Teaching Experience}
\begin{itemize} \setlength\itemsep{0.01em}
                          \item Quantitative Methods in Economics (\textit{tutorials and lectures}) WS/2018-2022  
                          \item Advanced Microeconomics (\textit{tutorials}) WS/2018-2022 
                          \item Microeconomics II (Game Theory) (\textit{tutorials}) SS/2019, 2021 
\end{itemize}

\noindent I'm writing a concise and intuitive text for new graduate students in need of revising their math, see \href{https://cloud.uni-konstanz.de/index.php/s/nSm3TmENpPX3q6C}{\textcolor{blue}{here}}.

\subsection*{Software Skills}

\LaTeX, R, Git, GitHub, Office \\

\noindent I develop tools for efficient use of Statistics Finland data, see in \href{https://github.com/jalasalmi}{\textcolor{blue}{GitHub}}.



\subsection*{Work and Education}
\begin{tabular}{@{}p{1.5in}p{5in}}
10/2018 - 8/2023   & Ph.D. Candidate, Graduate School of Decision Sciences, University of Konstanz \\
10/2018 - 8/2023  & Teaching and research assistant, Chair of Microeconomic Theory,  University of Konstanz \\

                                                 
\\
9/2018 -            & Economist, Pellervo Economic Research\\

\\
6/2018 - 9/2018 & Intern, Pellervo Economic Research\\

\\
8/2016 - 7/2018 & Master's Degree Programme in Public Economics and Public Finance, University of Tampere/University of Fribourg, \textit{Summa cum laude}. Master's Thesis: \textit{Motivated Prospects of Upward Mobility} \href{http://urn.fi/URN:NBN:fi:uta-201807022210}{\textcolor{blue}{http://urn.fi/URN:NBN:fi:uta-201807022210}}\\

\\
4/2017 - 9/2017 & Student research assistant, Chair of Microeconomic Theory,  University of Konstanz\\

\\
3/2016 - 8/2017 & University of Konstanz, Erasmus exchange \\
\\
8/2013 - 7/2016 & Bachelor of Science (Economics and Business Administration), University of Tampere\\
                           
\end{tabular}
%
%\subsection*{Relevant work experience}
%\begin{tabular}{@{}p{1.5in}p{5in}}
%10/2018 -            & Teaching and research assistant, Chair of Microeconomic Theory,  University of Konstanz \\
%                          &   -  Quantitative Methods in Economics (\textit{tutorials and lectures}) WS/2018-2022  \\
%                          &   -  Advanced Microeconomics (\textit{tutorials}) WS/2018-2022 \\   
%                          &   -  Microeconomics II (Game Theory) (\textit{tutorials}) SS/2019, 2021 \\   
%                                                 
%\\
%9/2018 -            & Economist, Pellervo Economic Research\\
%
%\\
%6/2018 - 9/2018 & Intern, Pellervo Economic Research\\
%
%\\
%4/2017 - 9/2017 & Student research assistant, Chair of Microeconomic Theory,  University of Konstanz\\
%                           
%\end{tabular}
%
%\subsection*{Relevant Education}
%\begin{tabular}{@{}p{1.5in}p{5in}}
%10/2018 -          & PhD Candidate, Graduate School of Decision Sciences, University of Konstanz \\
%                        
%\\
%8/2016 - 7/2018 & Master's Degree Programme in Public Economics and Public Finance, University of Tampere/University of Fribourg, \textit{Summa cum laude}. Master's Thesis: \textit{Motivated Prospects of Upward Mobility} \href{http://urn.fi/URN:NBN:fi:uta-201807022210}{\textcolor{blue}{http://urn.fi/URN:NBN:fi:uta-201807022210}}\\
%\\
%3/2016 - 8/2017 & University of Konstanz, Erasmus exchange \\
%\\
%8/2013 - 7/2016 & Bachelor of Science (Economics and Business Administration), University of Tampere\\
%%\\
%%1/2012 - 1/2013 & Mandatory military service, rank: second lieutenant\\
%%\\
%%8/2008 - 12/2011 & Finnish matriculation examination, Kajaanin lukio
%\end{tabular}



\subsection*{Conference \& Seminar presentations}
\begin{tabular}{@{}p{1.5in}p{5in}}
8/2018             & GSDS Conference on Decision Sciences, Konstanz,\\
4/2019             & European Public Choice Society Meeting, Jerusalem\\
5/2019             & TWI Microseminar, Kreuzlingen \\
6/2019             & Genova Summer School of Political Economy, Genova \\
8/2019             & International Institute of Public Finance Annual Conference, Glasgow \\
10/2019           & 1st Spanish Public Choice Workshop, Pamplona \\
1/2020             & Winter School on Inequality and Social Welfare Theory, Alba di Canazei \\
1/2020             & Perspectives on (un-)employment, 12th Ph.D. Workshop, IAB, Nuremberg \\
8/2020             & International Institute of Public Finance Video Conference \\
4/2021             & European Public Choice Society Meeting, Lille \\
8/2021             & International Institute of Public Finance Annual Congress, Reykjavik \\
3/2022             & Public Choice Society Meeting, Nashville \\
4/2022             & European Public Choice Society Meeting, Braga \\
5/2022             & Workshop "Motivated Beliefs", Kreuzlingen \\
6/2022             & 38. Annual summer meeting of Finnish research economists, Jyväskylä \\
7/2022             & CEMIR Junior Economist Workshop on Migration Research, Munich \\
8/2022             & RUCAM Workshop on Analytical Modelling Approaches to Understanding Democracy, Nijmegen \\
9/2022             &  37th National Conference of Labour Economics, Salerno
\end{tabular}

\subsection*{Research Funding and Grants}

\begin{tabular}{@{}p{1.5in}p{5in}}
11/2019  & Ty\"{o}politiikan vaikuttavuuden meta-analyysi (Meta-analysis of the Effects of Labour Market Policy) Prime Minister's Office (150 000 euro, Co-I) \\
1/2021    & Ammatillisen ty\"{o}voimakoulutuksen toimivuuden ja vaikutusten arviointi (Evaluation of Vocational Labour Market Training) Prime Minister's Office (150 000 euro, Co-I) \\
10/2021  & Aktiivisen työvoimapolitiikan palveluiden kustannusvaikuttavuus (The Cost-effectiveness of Active Labour Market Policies) Audit Committee of Parliament of Finland (100 000 euro, Co-I)\\
12/2021   & Osaajapula ja kohtaanto (Skill Deficits and Matching in Labour Markets) Akava ry (35 000 euro, Co-I)\\
9/2022   & Selvitys kotoutumiskoulutukseen osallistuneiden työllistymisestä, siirtymäajoista ja palvelupoluista (Investigation of Participants' Inflow into Integration Training for Immigrants and Employment Outcomes) Ministry of Employment and Economic Affairs (30 000 euro, Co-I) 
\end{tabular}



\subsection*{Language skills}
Finnish (native), English (proficient), German (good), Swedish (forgotten)

\subsection*{Publications in Finnish}

\noindent Ammatillisen työvoimakoulutuksen vaikuttavuus 2005-2017 \\
\noindent (Effectiveness of Vocational Labour Market Training in 2005–2017) \\
\noindent  with Henna Buck and Veera Holappa. \textit{Työpoliittinen aikakauskirja (Finnish Labour Review)} 3/2022 vol. 63, 24-36.  (2022). \href{https://tem.fi/julkaisu?pubid=URN:ISBN:978-952-327-910-0}{\textcolor{blue}{https://tem.fi/julkaisu?pubid=URN:ISBN:978-952-327-910-0f}} \\

\noindent Aktiivisen työvoimapolitiikan palveluiden kustannusvaikuttavuus \\
\noindent (The Cost-effectiveness of Active Labour Market Policies) \\
\noindent with Henna Buck, Veera Holappa, Olli Oosi and Antti Raukola. \textit{Eduskunnan tarkastusvaliokunnan julkaisu 2/2022} (2022). \href{https://www.eduskunta.fi/FI/naineduskuntatoimii/julkaisut/Documents/TrVJ\_2\_2022\_tyovoimapolitiikan\_palvelut.pdf}{\textcolor{blue}{https://www.eduskunta.fi/FI/naineduskuntatoimii/julkaisut/Documents/TrVJ\_2\_2022\_tyovoimapolitiikan\_palvelut.pdf}} \\

\noindent Ammatillisen ty\"{o}voimakoulutuksen toimivuuden ja vaikutusten arviointi \\
\noindent (Evaluation of Vocational Labour Market Training) \\
\noindent with Henna Busk, Veera Holappa, Hannu Karhunen, Minna Mayer, Annika Nivala, Tuomo Suhonen, Mikko Valtakari.  \textit{Valtioneuvoston selvitys- ja tutkimustoiminnan julkaisusarja} 2022:35 (2022). \href{http://urn.fi/URN:ISBN:978-952-383-008-0}{\textcolor{blue}{http://urn.fi/URN:ISBN:978-952-383-008-0}} \\

\noindent Ovatko ty\"{o}tt\"{o}myysturvan kokonaisvaikutukset yksil\"{o}vaikutusten summa? \\
\noindent (Do the Micro Effects of Unemployment Insurance Scale up to Macro Effects?) \\
\noindent  \textit{Ty\"{o}poliittinen aikakauskirja (Finnish Labour Review)} 4/2020 vol. 63, 11-21.  (2020). \\ \href{https://tem.fi/julkaisu?pubid=URN:ISBN:978-952-327-583-6} {\textcolor{blue}{https://tem.fi/julkaisu?pubid=URN:ISBN:978-952-327-583-6}}\\

\noindent Alueiden v\"{a}linen ty\"{o}ss\"{a}k\"{a}ynti ja ty\"{o}per\"{a}inen monipaikkainen asuminen Suomessa \\
\noindent (Interregional Commuting and Labour Related Multilocal Living in Finland) \\
\noindent with Ossi Kotavaara, Olli Lehtonen, Janne Huovari, Niina Kotavaara. \textit{Alue ja ympäristö} vol 49 nro 1 69-86 (2020) \href{https://aluejaymparisto.journal.fi/article/view/85160/54065}{\textcolor{blue}{https://aluejaymparisto.journal.fi/article/view/85160/54065}} \\
 
\noindent Ty\"{o}tt\"{o}myysturvaj\"{a}rjestelm\"{a} \\
\noindent (The Unemployment Insurance System) \\
\noindent with Henna Busk. Raportissa Ty\"{o}politiikka ja ty\"{o}llisyysaste: tutkimukseen perustuvia johtop\"{a}\"{a}t\"{o}ksi\"{a}. \textit{Valtioneuvoston selvitys- ja tutkimustoiminnan julkaisusarja} 2020:33 (2020) \href{http://urn.fi/URN:ISBN:978-952-287-951-6}{\textcolor{blue}{http://urn.fi/URN:ISBN:978-952-287-951-6}} \\

\noindent Osaamisen kehitt\"{a}miseen t\"{a}ht\"{a}\"{a}v\"{a}t ty\"{o}voimapalvelut vaikuttavat tehokkaimmin ty\"{o}llistymiseen \\
\noindent (Active Labour Market Policies Focusing on Increasing Skills Have Strongest Employement Effects) \\
\noindent with Henna Busk. Teoksessa Työttömien näkökulmia elinikäiseen oppimiseen. Sinimaaria Ranki (toim.) (2020) \href{https://www.sitra.fi/julkaisut/tyottomien-nakokulma-elinikaiseen-oppimiseen/}{\textcolor{blue}{https://www.sitra.fi/julkaisut/tyottomien-nakokulma-elinikaiseen-oppimiseen/}} \\

\noindent Ty\"{o}n ja ty\"{o}voiman alueellinen liikkuvuus ja monipaikkainen v\"{a}est\"{o} \\
\noindent (Regional Mobility of Work and Workers and Multilocal Population) \\
\noindent with Henna Busk, Veera Holappa, Janne Huovari, Valtteri H\"{a}rm\"{a}l\"{a}, Ossi Kotavaara, Olli Lehtonen, Toivo Muilu, Hilkka Vihinen, Jarmo Rusanen. \textit{Valtioneuvoston selvitys- ja tutkimustoiminnan julkaisusarja} 2020:12. (2020) \href{http://urn.fi/URN:ISBN:978-952-287-928-8}{\textcolor{blue}{http://urn.fi/URN:ISBN:978-952-287-928-8}} \\

\noindent Katsaus aktiivisen ty\"{o}voimapolitiikan vaikuttavuuteen \\
\noindent (Review of the Impact of Active Labour Market Policy Measures) \\
\noindent with Henna Busk. \textit{Ty\"{o}poliittinen aikakauskirja (Finnish Labour Review)} 3/2019 vol. 62, 11-21.  (2019) \\
\noindent \href{http://urn.fi/URN:ISBN:978-952-327-446-2}{\textcolor{blue}{http://urn.fi/URN:ISBN:978-952-327-446-2}} \\

\noindent Ty\"{o}voimapoliittisten toimenpiteiden kustannusvaikuttavuus \\
\noindent (Costs and Benefits of Labour Market Policy Measures) \\
\noindent with Naufal Alimov. \textit{Ty\"{o}poliittinen aikakauskirja (Finnish Labour Review)} 1/2019 vol. 62, 38-49.  (2019) \\
\noindent \href{http://urn.fi/URN:ISBN:978-952-287-645-4}{\textcolor{blue}{http://urn.fi/URN:ISBN:978-952-327-418-1}} \\

\noindent Ty\"{o}tt\"{o}myyden laajat kustannukset yhteiskunnalle \\
\noindent (The Societal Costs of Unemployment) \\
\noindent with Laura Ansala, Naufal Alimov, Henna Busk, Ville-Vallteri Huhtala, Antti Kek\"{a}l\"{a}inen, Peetu Keskinen, Olli-Pekka Ruuskanen, Lauri Vuori.  \textit{Valtioneuvoston selvitys- ja tutkimustoiminnan julkaisusarja} 16/2019 (2019). \href{http://urn.fi/URN:ISBN:978-952-287-645-4}{\textcolor{blue}{http://urn.fi/URN:ISBN:978-952-287-645-4}} \\




%\subsection*{Language skills}
%Finnish (native), English (proficient), German (good), Swedish (forgotten)
%
%\subsection*{Software skills}
%MS Office, MatLab, R, \LaTeX, Git, Github
%
%\subsection*{Positions of responsibility}
%\begin{tabular}{@{}p{1.5in}p{5in}}
%1/2015 - 12/2016 & The member of board and representative of educational affairs of economics student association Pareto ry\\
%1/2016 - 12/2016 & The member of board and the vice president of the debate society UTA Debate Society\\
%\end{tabular}
%






\end{document}